### 2024-03-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: study_session_20240225.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="study_session_20240225_files/md-default3.js" type="text/javascript"></script><script src="study_session_20240225_files/md-default4.js" type="text/javascript"></script>

@@

```{=html}
<img src="study_session_20240225_files/0.png" style="width:100%;" />
```

@@

_unnamed [234 11]:

@@

@@

```{=html}
<img src="study_session_20240225_files/1.png" style="width:100%;" />
```

@@

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [[$ .MEM xfeea946278794b6e]],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ year]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["year"]}}

@@

::: {.sourceClojure}
```clojure
(-> toydata.ggplot/mpg
    (gg/ggplot (gg/aes :x 'cty
                       :y 'hwy
                       :color 'year))
    (r/r+ (gg/geom_point)
          (gg/scale_y_log10))
    r
    plotting/plot->buffered-image)
```
:::

```{=html}
<img src="study_session_20240225_files/2.png" style="width:100%;" />
```

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: study_session_20240225.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style><style>.clay-limit-image-width .clay-image {max-width: 100%}
</style>
<script src="study_session_20240225_files/md-default2.js" type="text/javascript"></script><script src="study_session_20240225_files/md-default3.js" type="text/javascript"></script>

@@

::: {.clay-image}

```{=html}
<img src="study_session_20240225_files/0.png" />
```

:::

@@

::: {.clay-dataset}
_unnamed [234 11]:

@@

:::

@@

::: {.clay-image}

```{=html}
<img src="study_session_20240225_files/1.png" />
```

:::

@@

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [[$ .MEM x861a15f64ba24c00]],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ year]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["year"]}}

@@

::: {.sourceClojure}
```clojure
(-> toydata.ggplot/mpg
    (gg/ggplot (gg/aes :x 'cty
                       :y 'hwy
                       :color 'year))
    (r/r+ (gg/geom_point :size 5)
          (gg/scale_y_log10))
    r
    plotting/plot->svg
    kind/html)
```
:::

```{=html}
<?xml version="1.0" encoding="UTF-8"?>
<svg xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink" width="504pt" height="504pt" viewBox="0 0 504 504" version="1.1">
<defs>
<g>
<symbol overflow="visible" id="glyph0-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph0-1">
<path style="stroke:none;" d="M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph0-2">
<path style="stroke:none;" d="M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 "/>
</symbol>
<symbol overflow="visible" id="glyph0-3">
<path style="stroke:none;" d="M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 "/>
</symbol>
<symbol overflow="visible" id="glyph0-4">
<path style="stroke:none;" d="M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-5">
<path style="stroke:none;" d="M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 "/>
</symbol>
<symbol overflow="visible" id="glyph0-6">
<path style="stroke:none;" d="M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-7">
<path style="stroke:none;" d="M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-8">
<path style="stroke:none;" d="M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 "/>
</symbol>
<symbol overflow="visible" id="glyph1-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph1-1">
<path style="stroke:none;" d="M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-2">
<path style="stroke:none;" d="M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-3">
<path style="stroke:none;" d="M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-4">
<path style="stroke:none;" d="M 5.640625 -2.578125 C 5.640625 -3.453125 5.578125 -3.984375 5.40625 -4.40625 C 5.03125 -5.359375 4.15625 -5.921875 3.078125 -5.921875 C 1.46875 -5.921875 0.4375 -4.703125 0.4375 -2.8125 C 0.4375 -0.90625 1.4375 0.25 3.0625 0.25 C 4.375 0.25 5.296875 -0.5 5.515625 -1.75 L 4.59375 -1.75 C 4.34375 -0.984375 3.828125 -0.59375 3.09375 -0.59375 C 2.515625 -0.59375 2.015625 -0.859375 1.703125 -1.34375 C 1.484375 -1.671875 1.40625 -2 1.390625 -2.578125 Z M 1.421875 -3.328125 C 1.5 -4.390625 2.140625 -5.078125 3.0625 -5.078125 C 4 -5.078125 4.65625 -4.359375 4.65625 -3.328125 Z M 1.421875 -3.328125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-5">
<path style="stroke:none;" d="M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-6">
<path style="stroke:none;" d="M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph2-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph2-1">
<path style="stroke:none;" d="M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph2-2">
<path style="stroke:none;" d="M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 "/>
</symbol>
<symbol overflow="visible" id="glyph2-3">
<path style="stroke:none;" d="M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 "/>
</symbol>
</g>
<clipPath id="clip1">
  <path d="M 35.152344 5.480469 L 433.84375 5.480469 L 433.84375 469.851562 L 35.152344 469.851562 Z M 35.152344 5.480469 "/>
</clipPath>
<clipPath id="clip2">
  <path d="M 35.152344 414 L 433.84375 414 L 433.84375 415 L 35.152344 415 Z M 35.152344 414 "/>
</clipPath>
<clipPath id="clip3">
  <path d="M 35.152344 348 L 433.84375 348 L 433.84375 349 L 35.152344 349 Z M 35.152344 348 "/>
</clipPath>
<clipPath id="clip4">
  <path d="M 35.152344 216 L 433.84375 216 L 433.84375 218 L 35.152344 218 Z M 35.152344 216 "/>
</clipPath>
<clipPath id="clip5">
  <path d="M 35.152344 104 L 433.84375 104 L 433.84375 105 L 35.152344 105 Z M 35.152344 104 "/>
</clipPath>
<clipPath id="clip6">
  <path d="M 101 5.480469 L 103 5.480469 L 103 469.851562 L 101 469.851562 Z M 101 5.480469 "/>
</clipPath>
<clipPath id="clip7">
  <path d="M 171 5.480469 L 173 5.480469 L 173 469.851562 L 171 469.851562 Z M 171 5.480469 "/>
</clipPath>
<clipPath id="clip8">
  <path d="M 241 5.480469 L 242 5.480469 L 242 469.851562 L 241 469.851562 Z M 241 5.480469 "/>
</clipPath>
<clipPath id="clip9">
  <path d="M 310 5.480469 L 312 5.480469 L 312 469.851562 L 310 469.851562 Z M 310 5.480469 "/>
</clipPath>
<clipPath id="clip10">
  <path d="M 380 5.480469 L 382 5.480469 L 382 469.851562 L 380 469.851562 Z M 380 5.480469 "/>
</clipPath>
<clipPath id="clip11">
  <path d="M 35.152344 282 L 433.84375 282 L 433.84375 284 L 35.152344 284 Z M 35.152344 282 "/>
</clipPath>
<clipPath id="clip12">
  <path d="M 35.152344 150 L 433.84375 150 L 433.84375 152 L 35.152344 152 Z M 35.152344 150 "/>
</clipPath>
<clipPath id="clip13">
  <path d="M 35.152344 57 L 433.84375 57 L 433.84375 59 L 35.152344 59 Z M 35.152344 57 "/>
</clipPath>
<clipPath id="clip14">
  <path d="M 66 5.480469 L 68 5.480469 L 68 469.851562 L 66 469.851562 Z M 66 5.480469 "/>
</clipPath>
<clipPath id="clip15">
  <path d="M 136 5.480469 L 138 5.480469 L 138 469.851562 L 136 469.851562 Z M 136 5.480469 "/>
</clipPath>
<clipPath id="clip16">
  <path d="M 206 5.480469 L 208 5.480469 L 208 469.851562 L 206 469.851562 Z M 206 5.480469 "/>
</clipPath>
<clipPath id="clip17">
  <path d="M 275 5.480469 L 277 5.480469 L 277 469.851562 L 275 469.851562 Z M 275 5.480469 "/>
</clipPath>
<clipPath id="clip18">
  <path d="M 345 5.480469 L 347 5.480469 L 347 469.851562 L 345 469.851562 Z M 345 5.480469 "/>
</clipPath>
<clipPath id="clip19">
  <path d="M 415 5.480469 L 417 5.480469 L 417 469.851562 L 415 469.851562 Z M 415 5.480469 "/>
</clipPath>
<clipPath id="clip20">
  <path d="M 450.28125 203.203125 L 467.5625 203.203125 L 467.5625 289.601562 L 450.28125 289.601562 Z M 450.28125 203.203125 "/>
</clipPath>
<image id="image486" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>
<pattern id="pattern0" patternUnits="userSpaceOnUse" width="1" height="300"  patternTransform="matrix(17.28,0,0,0.288,450.281644,203.20411)">
  <use xlink:href="#image486"/>
</pattern>
</defs>
<g id="surface482">
<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
<rect x="0" y="0" width="504" height="504" style="fill:rgb(100%,100%,100%);fill-opacity:1;stroke:none;"/>
<path style="fill:none;stroke-width:1.066978;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 0 504 L 504 504 L 504 0 L 0 0 Z M 0 504 "/>
<g clip-path="url(#clip1)" clip-rule="nonzero">
<path style=" stroke:none;fill-rule:nonzero;fill:rgb(92.156863%,92.156863%,92.156863%);fill-opacity:1;" d="M 35.152344 469.847656 L 433.84375 469.847656 L 433.84375 5.476562 L 35.152344 5.476562 Z M 35.152344 469.847656 "/>
</g>
<g clip-path="url(#clip2)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 414.507812 L 433.84375 414.507812 "/>
</g>
<g clip-path="url(#clip3)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 348.636719 L 433.84375 348.636719 "/>
</g>
<g clip-path="url(#clip4)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 216.898438 L 433.84375 216.898438 "/>
</g>
<g clip-path="url(#clip5)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 104.289062 L 433.84375 104.289062 "/>
</g>
<g clip-path="url(#clip6)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 102.0625 469.847656 L 102.0625 5.480469 "/>
</g>
<g clip-path="url(#clip7)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 171.765625 469.847656 L 171.765625 5.480469 "/>
</g>
<g clip-path="url(#clip8)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 241.46875 469.847656 L 241.46875 5.480469 "/>
</g>
<g clip-path="url(#clip9)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 311.167969 469.847656 L 311.167969 5.480469 "/>
</g>
<g clip-path="url(#clip10)" clip-rule="nonzero">
<path style="fill:none;stroke-width:0.533489;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 380.871094 469.847656 L 380.871094 5.480469 "/>
</g>
<g clip-path="url(#clip11)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 282.765625 L 433.84375 282.765625 "/>
</g>
<g clip-path="url(#clip12)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 151.027344 L 433.84375 151.027344 "/>
</g>
<g clip-path="url(#clip13)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 35.152344 57.554688 L 433.84375 57.554688 "/>
</g>
<g clip-path="url(#clip14)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 67.214844 469.847656 L 67.214844 5.480469 "/>
</g>
<g clip-path="url(#clip15)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 136.914062 469.847656 L 136.914062 5.480469 "/>
</g>
<g clip-path="url(#clip16)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 206.617188 469.847656 L 206.617188 5.480469 "/>
</g>
<g clip-path="url(#clip17)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 276.316406 469.847656 L 276.316406 5.480469 "/>
</g>
<g clip-path="url(#clip18)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 346.019531 469.847656 L 346.019531 5.480469 "/>
</g>
<g clip-path="url(#clip19)" clip-rule="nonzero">
<path style="fill:none;stroke-width:1.066978;stroke-linecap:butt;stroke-linejoin:round;stroke:rgb(100%,100%,100%);stroke-opacity:1;stroke-miterlimit:10;" d="M 415.722656 469.847656 L 415.722656 5.480469 "/>
</g>
<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 184.425781 162.042969 C 184.425781 165.183594 181.878906 167.730469 178.734375 167.730469 C 175.59375 167.730469 173.046875 165.183594 173.046875 162.042969 C 173.046875 158.898438 175.59375 156.351562 178.734375 156.351562 C 181.878906 156.351562 184.425781 158.898438 184.425781 162.042969 "/>
<path style="fill-rule:nonzero;fill:rgb(7.45098%,16.862745%,26.27451%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(7.45098%,16.862745%,26.27451%);stroke-opacity:1;stroke-miterlimit:10;" d="M 226.246094 162.042969 C 226.246094 165.183594 223.699219 167.730469 220.558594 167.730469 C 217.414062 167.730469 214.867188 165.183594 214.867188 162.042969 C 214.867188 158.898438 217.414062 156.351562 220.558594 156.351562 C 223.699219 156.351562 226.246094 158.898438 226.246094 162.042969 "/>
<path style="fill-rule:nonzero;fill:rgb(33.72549%,69.411765%,96.862745%);fill-opacity:1;stroke-width:0.708661;stroke-linecap:round;stroke-linejoin:round;stroke:rgb(33.72549%,69.411765%,96.862745%);stroke-opacity:1;stroke-miterlimit:10;" d="M 212.304688 140.371094 C 212.304688 143.515625 209.757812 146.0625 206.617188 146.0625 C 203.472656 146.0625 200.925781 143.515625 200.925781 140.371094 C 200.925781 137.230469 203.472656 134.683594 206.617188 134.683594 C 209.757812 134.683594 212.304688 137.230469 212.304688 140.371094 "/>
